An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-18 draft.tex
first draft of the proposed method  intro

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEO}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

@@

\subsection{Event Driven Model} 
\label{edm}
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure \ref{fig:kafkEO}. Again, we can explain the general model using the analogy
of Producers and Consumers of messages using a queue. First, we can see that
there are two queues, one labeled Input, and the other one Output. In the diagram, 
push operations on a queue are represented by solid arrows connecting to the left side
of the box, and pull or pop operations as solid arrows leaving from the right side.

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{kafkEOsmall}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

@@

\subsection{Event Driven Model} 
\label{edm}
Based on a reactive architecture we proposed in a previous work
\cite{guervos2018introducing}, we now describe the general architecture shown in
Figure \ref{fig:kafkEO}. Again, we can explain the model using the analogy
of Producers and Consumers of messages. First, we can see that
there are two queues, one labeled Input, and the other one Output. In the diagram, 
push operations on a queue are represented by solid arrows connecting to the left side
of the box, and pull or pop operations as solid arrows leaving from the right side.
The algorithm starts with the Setup process pulling a configuration message from
the experiements queue, this is not shown in the diagram. The configuration messsage 
includes all the parameters needed to execute the algorithm, among other things,
the number of subpopulations, the number of individuals, and the number of iterations
of the algorithm. We give more details about the configuration data structure
in Section []. Once the configuration is read, we can follow the path of 
messagess as follows:

\begin{enumerate}
\item In this step, the specified number of subpopulations is created acording to the 
parameters found in the configuration structure. The population at this moment is just
static data, including each individual inside. Each subpopulation includes a metadata
section where its algorithm and execution parameters are specified. For instance, 
for a GA, the mutation rate, type of crossover operator, and other values are indicated.
Each subpopulation is then pushed to the Input queue, so they can be consumed 
by Stateless functions responsible for the execution of the search.

\item One or more Stateless functions are constantly pulling subpopulation messages
from the Input queue. Taking the population data and metadata as parameters, these 
functions are responsible for the actual execution of the optimization algorithm. 
They take the current state of the population and run the algorithm for a certain 
number of iterations. Once they finish the execution, the population state
is packed again along with aditional metadata about the execution of the algorithm.
The resulting populations is now pushed to the Output queue. Once finished, another 
subpopulation is pulled from the queue.

\item The Controller process is responsible for keeping track of the progress of 
the search. It pulls current subpopulations from the Output queue, inspects the metadata 
and if an optimal solution has been found or the maximum number of iteration has been
reached it signals the stop of the execution. Otherwise, it passes the stream of messages 
to a migration process, where subpopulations are mixed with each other. New populations 
are generated from this migration, and they are again pushed to the Input queue to continue 
in a loop. The Controller is also responsible of logging the metadata recived with the
messages.

\end{enumerate}
